### 2023-03-04 manuscript.tex
Update environment.yml [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/c300807d221901c7441dc86e15a3e2c6c4d2f7c4.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/c300807d221901c7441dc86e15a3e2c6c4d2f7c4/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4333031977

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/540c54a0e1a9c1b107387aa297db8144b6a79d5e/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/540c54a0e1a9c1b107387aa297db8144b6a79d5e}{SORTEE-Github-Hackathon/manuscript@540c54a}
on March 4, 2023.

@@

\toprule

@@

\midrule

@@

\bottomrule

@@

Personal or laboratory websites can improve the sharing of research findings, build online presence, and increase coordination of research efforts (\protect\hyperlink{ref-HiIPSSHV}{Smaglik, 2007}).
Despite researchers in ecology and evolution generally lacking experience in building or hosting webpages, many tools have been developed to help this process.
Static websites can now be easily built {[}using, for example Quarto (\url{https://quarto.org}), RMarkdown, Hugo (\url{https://gohugo.io}), GitHub Website templates (\url{https://github.com/topics/website-template})), stored in a repository, and be readily hosted by activating GitHub's Pages (\url{https://pages.github.com}) feature.
Creating and hosting websites on GitHub Pages is more complex than out-of-the-box platforms (\emph{e.g.}, Wix, Weebly, Google Sites).
However, free hosting, widely available template customization, and versioning are strong advantages over alternatives.{]}.
Users can set up workflows associated with their repositories that are triggered by events (\emph{e.g.}, push, pull request or at specified times) for remote servers to perform user-specified steps and actions.
These actions are highly configurable and have numerous applications, such as automatically running analyses and creating figures when data or code are updated, incorporating changes to websites or applications, testing modifications to software (\emph{e.g.}, R or Python libraries).
Action workflows can be found in GitHub's Marketplace (\url{https://github.com/marketplace?type=actions}) or, alternatively, in open user repositories.

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.0000}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
Ten tips for getting started in GitHub
\end{minipage} \\
\midrule
\endhead
1. \textbf{Check for existing solutions to your problem.} The GitHub Help webpage (\url{https://docs.github.com/en}) contains extensive and detailed documents with helpful screenshots. It is a good starting point for handling an issue, and has troubleshooting tips for specific problems. Alternatively, consider Tweeting your issue. There is a large community of GitHub users around the world who have likely faced analogous problems and may be able to provide quick solutions. Third, try to follow blogs (\emph{e.g.}, \url{https://github.blog}), Twitter accounts or YouTube channels that regularly post practical solutions about the most widely-used web platform for common GitHub issues. \\
2. \textbf{Consider taking free courses}, such as those from Software Carpentry (\protect\hyperlink{ref-pjy75gHr}{Madicken Munk et al., 2019}), and sharing them with your lab members or colleagues. \\
3. \textbf{Take advantage of GitHub as an asynchronous working tool for team-based projects.} See the repository for this paper (\url{https://github.com/SORTEE-Github-Hackathon/manuscript}) as an example of a collaboratively authored manuscript that used the GitHub Discussions, Issues, Pages, and Actions features. \\
4. \textbf{Use the interactive courses from the GitHub Skills page (\url{https://skills.github.com/})}, which allow you to learn GitHub basics through short projects and tasks with step-by-step guides. \\
5. \textbf{Learn markdown and use cheatsheets (\emph{e.g.}, \url{http://markdownguide.org/basic-syntax})} so you can write clear metadata README files for your repositories. \\
6. \textbf{Consult online resources.} The Jenny Bryan Universe of GitHub material, for example, provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book (\protect\hyperlink{ref-ZvrOcg9w}{Hester, n.d.}), statistics course (\protect\hyperlink{ref-6CMMeSeD}{Bryan \& TAs, n.d.}) and academic article (\protect\hyperlink{ref-RVetqmsg}{Bryan, 2018}). \\
7. \textbf{Do not be afraid of trial-and-error.} One of the best ways to learn GitHub is the ``trial-and-error'' method. Learning from your own mistakes can be a valuable way to master your GitHub abilities. In any case, if you make mistakes, GitHub allows you to revert any steps that you desire via version controlling. \\
8. \textbf{If you are an educator, include lectures on reproducibility and tools for creating reproducible workflows in the curricula.} Some graduate programs include coursework on course R Markdown and GitHub. Getting students started with these tools earlier will prevent the resistance that comes from working with a less reproducible workflow for a longer period of time (see example \url{https://github.com/rmcelreath/stat_rethinking_2022}). \\
9. \textbf{Try to begin committing with graphical user interfaces (GUI) instead of command line interfaces (CLI).} Examples of GUI are the GitHub Desktop (\url{https://desktop.github.com}), git-gui (\url{https://git-scm.com/docs/git-gui}), RStudio (\url{https://www.rstudio.com}), Visual Studio Code (\url{https://code.visualstudio.com}), Atom (\url{https://atom.io}), GitKraken (\url{https://www.gitkraken.com}). \\
10. \textbf{Get help deciphering GitHub Notifications.} Try using tools like Octobox (\url{https://octobox.io}) to disentangle and manage multiple notifications from distinct GitHub projects. \\
\bottomrule
\end{longtable}

@@

\caption{A comparison of technologies commonly used for collaborating on research in Ecology and Evolutionary Biology. In the first column, we group platforms for collaboration into broad guilds. The second column lists the platform for collaboration. The remaining columns indicate whether the platform for collaboration includes certain features. \label{tbl:compare}}\tabularnewline
\toprule

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0493}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1425}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1041}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1562}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1096}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1479}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1370}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1534}}@{}}
\caption{A non-exhaustive collection of ideas for how various GitHub
features could be utilized for a research project. Here we have
categorized contributors/collaborators into five roles. A Project
Manager owns the GitHub repository for a project, and leads the academic
project (e.g., lead author of a manuscript). A co-author contributes to
writing and other aspects of research, but may have limited or no
experience with programming, git, and/or GitHub. A code contributor
writes or edits analysis code for the project. A code reviewer could be
a project collaborator or a peer reviewer who reviews project code. They
are familiar with coding, but not necessarily with git or GitHub (but
they are willing to learn). Finally, community members could be other
researchers or non-researchers interested in reproducing results,
re-using code or data, or communicating with researchers involved in the
project. These roles are not mutually exclusive---a co-author could also
be a code contributor and code reviewer, for example. For definitions of
the GitHub features, see Box 1. \label{tbl:roles}}\tabularnewline
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
Role
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
GitHub repository
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
README
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Issue
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Discussion
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Pull Request
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Fork
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
GitHub Pages
\end{minipage} \\
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
Role
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
GitHub repository
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
README
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Issue
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Discussion
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Pull Request
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Fork
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
GitHub Pages
\end{minipage} \\
\midrule
\endhead
Project manager & Set contributor permissions, share code of conduct & Project description, citation, DOIs & Assign tasks to collaborators & Discuss project directions and goals & Approve and incorporate edits to code and/or writing & & Share up-to-date reports, figures, or draft manuscript \\
Co-author & Edit Markdown text or add files & & Propose changes involving code (e.g.~analyses, figures) & Discuss proposed changes to manuscript & & & \\
Code contributor & & & Suggest code changes & & Contribute changes to code, initiate code review & & Contribute to project website \\
Code reviewer & Find all code related to a project & & Highlight specific lines of code and make suggestions & & Review or recommended changes in code & & \\
Community & & & Suggest additional features and report bugs & Ask questions about data and code & & Create a linked, editable copy of the repository & View project website \\
\bottomrule
\end{longtable}

@@

\leavevmode\vadjust pre{\hypertarget{ref-13QX8XU3J}{}}%
Alston, J. M., \& Rick, J. A. (2021). A Beginner's Guide to Conducting Reproducible Research. \emph{The Bulletin of the Ecological Society of America}, \emph{102}(2). \url{https://doi.org/10.1002/bes2.1801}

@@

@@

@@

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/c300807d221901c7441dc86e15a3e2c6c4d2f7c4/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/c300807d221901c7441dc86e15a3e2c6c4d2f7c4}{SORTEE-Github-Hackathon/manuscript@c300807}
on 2023-03-04.

@@

\toprule()

@@

\midrule()

@@

\bottomrule()

@@

Personal or laboratory websites can improve the sharing of research findings, build online presence, and increase coordination of research efforts (\protect\hyperlink{ref-HiIPSSHV}{Smaglik, 2007}).
Despite researchers in ecology and evolution generally lacking experience in building or hosting webpages, many tools have been developed to help this process.
Static websites can now be easily built {[}using, for example Quarto (\url{https://quarto.org}), RMarkdown, Hugo (\url{https://gohugo.io}), GitHub Website templates (\url{https://github.com/topics/website-template})), stored in a repository, and be readily hosted by activating GitHub's Pages (\url{https://pages.github.com}) feature.
Creating and hosting websites on GitHub Pages is more complex than out-of-the-box platforms (\emph{e.g.}, Wix, Weebly, Google Sites).
However, free hosting, widely available template customization, and versioning are strong advantages over alternatives.

\hypertarget{archiving-citable-code}{%
\subsubsection{Archiving citable code and data}\label{archiving-citable-code}}

Government, funding agencies, and publishers exercise rigorous open access data policies and mandates (\protect\hyperlink{ref-1Hcf13Q0k}{Nugroho et al., 2015}; \protect\hyperlink{ref-PLmDFZrm}{Tenopir et al., 2020}).
However, code and data sharing may be met by individual reluctance, temporary embargoes, or partially prevented by privacy and confidentiality reasons (\protect\hyperlink{ref-SLq38RVv}{Figueiredo, 2017}; \protect\hyperlink{ref-1CzUZwyU2}{Tenopir et al., 2015}; \protect\hyperlink{ref-1Ch6LSHef}{Wicherts et al., 2011}).
Still, data deposition and ensuring its availability can amplify the outreach of published studies (\protect\hyperlink{ref-666HppfO}{Pronk et al., 2015}), increase citation rates (\protect\hyperlink{ref-1CcAUn3Lu}{Piwowar et al., 2007}), and among many other reasons, enable the reproducibility and robustness of scientific advances (\protect\hyperlink{ref-1HZdsK5Kn}{Baker, 2016}; \protect\hyperlink{ref-uBJwnPbq}{Mislan et al., 2016}; \protect\hyperlink{ref-4LaijDIZ}{{``On Data Availability, Reproducibility and Reuse,''} 2017}).
While public repositories on GitHub make it easy to store and share data files, they are not considered long-term repositories for research materials.
This is because GitHub, a for-profit company, does not have long-term data availability guarantees, allowing users to delete or make repositories private after publication.
Also, GitHub does not issue Digital Object Identifiers (DOI) for content uploaded to their servers.
DOIs are persistent and citable unique alpha-numeric identifiers assigned to digitally-stored research materials.
Because of this, scientists sharing code and data through GitHub are strongly encouraged to independently submit their research materials to long-term data archives (\emph{e.g.}, Zenodo, Figshare, Dryad, OSF (\protect\hyperlink{ref-1Du6fzB8g}{Crystal‐Ornelas et al., 2021}; \protect\hyperlink{ref-kEX5dgzK}{Perez-Riverol et al., 2016}; \protect\hyperlink{ref-10ghgV3S8}{J. Perkel, 2016}); \protect\hyperlink{tbl:compare}{Table 1}).
Some of these options (Zenodo, Figshare and OSF) integrate with GitHub, allowing project, code, and data releases (\protect\hyperlink{definitions}{Box 1}) to be archived with versioned, citable DOIs.
Linking GitHub repositories with a DOI helps research become findable, properly cited, and can ensure long-term stability (\protect\hyperlink{ref-iIEKCTLU}{Hampton et al., 2015}).
This strategy has been increasingly adopted in numerous studies in ecology and evolution (\emph{e.g.}, the Zenodo repositores for Hudgins (\protect\hyperlink{ref-GQj3c17f}{2022}), EllenJCoombs (\protect\hyperlink{ref-bZNn2hbh}{2020}), and Lrharper1 (\protect\hyperlink{ref-ZI1OqZNr}{2018})).

An important aspect of making code and data citable and reusable is to add an appropriate license to protect intellectual property.
Code published without a license is under exclusive copyright (by default), protecting it from copy, distribution, and modifications.
One may grant specific rights to their code for reuse by adding licensing files and specifications within GitHub repositories (\protect\hyperlink{ref-TOsASkn5}{\emph{Adding a License to a Repository}, n.d.}).
The Choose a License (\url{https://choosealicense.com/non-software/}) website offers further guidance on the licenses available for research and creative products.
For example, Creative Commons (CC; \url{https://creativecommons.org/licenses/}) licenses can specify that shared code is intended for a specific analysis.
A CC BY 4.0 license specifies that any code (or other creative products) must be appropriately credited to its original author when distributed, adapted or reused.

\hypertarget{code-editing}{%
\subsubsection{Collaborative and asynchronous code editing}\label{code-editing}}

GitHub can serve as a platform for everyone working with research (\emph{e.g.}, supervisors or advisors, graduate students, postdoctoral fellows, and collaborators) to share in-progress work, and flag specific challenges or questions for each other (\protect\hyperlink{tbl:roles}{Table 2}).
Periodic code, data and text review is useful for identifying errors early in the research process (\protect\hyperlink{ref-hm9PaCLD}{Song et al., 2020}), and informing further training and mentorship to fill gaps in skills.
This is facilitated by a group of core features of Git and GitHub that allow contributors to discuss and simultaneously work on a project.
For instance, users can clone and fork repositories (see \protect\hyperlink{definitions}{Box 1}), allowing for modifications to be done on a linked copy of a repository, which can then later be merged into the main project through pull requests.
Collaborators can comment on specific lines of code and text or suggest changes, which can then be incorporated with the click of a button, greatly facilitating peer review.
Explicit project organization and increased communication within pull requests, in GitHub Issues, or in GitHub Discussions can help with project development and with potential merge conflicts due to users simultaneously working on the same sections.
Moreover, version control allows researchers to make changes in code or documents without worrying about irreparably modifying someone else's work (\#storing-sharing).

By enabling more comprehensive remote collaboration, GitHub encourages the exchange of ideas among researchers at different institutions and in different countries, which can serve to improve the quality of the research itself by providing open access to data and code.

\hypertarget{writing-manuscript}{%
\subsubsection{Writing a manuscript}\label{writing-manuscript}}

Beyond supporting collaborative code development, GitHub can be used for writing manuscripts.
Writing a manuscript and storing its associated data and code in GitHub increases scientific reproducibility because text, code, and data can be found in one place.
Although it may involve more initial time investment for setup, GitHub has many features that support a powerful collaborative workflow when writing manuscripts (\protect\hyperlink{ref-4ny1onB0}{Ram, 2013}).
Text documents stored and versioned in GitHub can be instantly displayed when written in Markdown, a lightweight markup language increasingly popular among scientists.
When manuscripts are written in Markdown on GitHub, co-authors can contribute changes or suggest revisions to a manuscript in the same ways they would contribute changes or suggest revisions to code (see \protect\hyperlink{code-editing}{Collaborative and asynchronous code editing}).
Relevant literature or issues can be suggested using the Discussions and Issues features.

Incorporating GitHub into the process of writing a manuscript does not necessarily mean pivoting to an entirely new workflow.
For instance, authors who prefer writing in LaTeX or Markdown can synchronize Overleaf (\protect\hyperlink{ref-oGbKxHzj}{\emph{Using Git and GitHub}, n.d.}), HackMD (\url{https://hackmd.io}), and other platforms directly with a GitHub repository.
Similar GitHub integrations are available for projects stored in DropBox, Google Drive, among other popular tools familiar to many scientists and their collaborators (\protect\hyperlink{tbl:compare}{Table 1}).

We wrote this manuscript using Manubot, a modifiable workflow implemented in GitHub to automatically render manuscripts and automate bibliographical tasks (\protect\hyperlink{ref-YuJbg3zO}{Himmelstein et al., 2019}).
Manubot uses GitHub's automation workflow, GitHub Actions, to combine and convert individual Markdown files into a single LaTeX document, which can then be converted to a Word or PDF document, and displayed as a webpage.
Citations and bibliographic references are automatically managed with citable persistent identifiers (\emph{e.g.}, DOI, PubMed ID, ISBN, URL).
The resulting manuscript can be rendered with document templates and citation style language formatting to meet journal formatting requirements.
Every change made to the manuscript triggers its rendering, so that updates are readily displayed and made publicly available.
Additional GitHub Actions can be integrated with Manubot, such as ones creating figures or generating tables (\emph{e.g.}, \url{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/main/.github/workflows}).

\hypertarget{peer-review}{%
\subsubsection{Peer review}\label{peer-review}}

Peer review is the standard process for assessing whether research done in ecology and evolution should be published in a scientific journal.
GitHub provides an open and transparent platform that can be used for either directly providing feedback on research products or addressing changes recommended by reviewers.
GitHub Issues can be used to organize and discuss reviewer suggestions and to assign them to co-authors (\emph{e.g.}, \url{https://github.com/SORTEE-Github-Hackathon/manuscript/issues?q=label\%3A\%22Reviewer+Comment\%22}).
When reviewer comments are posted as separate issues, authors can comment on the issues to discuss possible changes and assign co-authors who will address the issue.
Co-authors can then integrate their edits and responses to reviewers using pull requests, which can be directly linked to the issues they address.

GitHub can also assist reviewers during the peer review process.
If the code associated with a manuscript is made available at the time of submission (\emph{e.g.}, as a link to a GitHub repository within the Data Availability Statement), peer reviewers may be able to offer more comprehensive suggestions on the code and written materials, potentially recognizing errors before publication.
Certain journals or software development communities require submitted work or research code to be hosted on GitHub and their review processes make use of GitHub Issues (\emph{e.g.}, rOpenSci (\url{https://ropensci.org/software-review/}), Journal of Open Source Software (\url{https://joss.readthedocs.io/en/latest/submitting.html}).

\hypertarget{open-science-discussion}{%
\subsubsection{Open science discussion}\label{open-science-discussion}}

Scientific publications often omit part of their intellectual and computational workflows, including the treatment of raw data and analytical steps (\emph{e.g.}, model assumption testing).
Publishing data and reproducible workflows along with manuscripts can provide readers with all details about analytical steps and enable reproducing research experiments and results (\protect\hyperlink{ref-NOgBWVAr}{Culina et al., 2020}).
In addition to storing data and code, GitHub repositories can provide a time-stamped (version controlled) preregistration of research plans and hypotheses.

Conventional research practices typically separate tasks among collaborators (\emph{i.e.}, data entry, analysis, writing).
It is common that coauthors discuss, but do not actively verify, edit, or execute research tasks that are not their main responsibility.
GitHub can serve as a tool for open and tractable research development.
Collaborators can directly interact with code and data, inspect for errors, and potentially identify scientific misconduct prior to manuscript submission (\emph{e.g.}, \url{https://ecologyforthemasses.com/2020/02/04/pruittdata-and-the-ethics-of-data-in-science}).
Collaborators and readers are better positioned to discover erroneous or questionable findings if they have complete and transparent access to projects.

This transparency can be extended beyond co-authors to the entire scientific community and to the public.
Supplying code for novel or currently used methods reduces barriers to knowledge, improving the ability of others to build on existing work.
This practice results in greater proliferation and accessibility for a broader audience.
Projects can make use of GitHub Discussions (\url{https://docs.github.com/en/discussions}) to communicate among repository members (collaborators) and to engage with other scientists and the general public.
Moreover, researchers can also use the GitHub Community (\url{https://github.community/}) forum to share expertise or request help from others on their analyses and ideas (\protect\hyperlink{tbl:roles}{Table 2}).

The desire or need for privacy during the developmental stages of a manuscript or of a larger research project is common in EEB, and this is often perceived as a major barrier to doing science openly.
Because GitHub repositories can be made private or public at any time, there is no need to choose privacy over open science, or vice-versa.
Repositories can be kept private until their contents are ready to be shared publicly, as might occur when a research article is published or when an embargo is lifted.

\hypertarget{automation}{%
\subsubsection{Automation}\label{automation}}

Automation has the strong potential to expand the scale and pace of research in ecology and evolution (\protect\hyperlink{ref-cfgXxgt1}{Keitt \& Abelson, 2021}).
Automation frameworks can streamline many stages of the scientific process, including data collection and data validation (\emph{e.g.}, \protect\hyperlink{ref-bhDgD6lF}{Micheletti et al., 2021}; \protect\hyperlink{ref-1CJo8lo2v}{Yenni et al., 2019}), data analysis (\emph{e.g.}, \protect\hyperlink{ref-Qh7xTLwz}{Beaulieu-Jones \& Greene, 2017}), unit testing of research code (\emph{e.g.}, \protect\hyperlink{ref-lYazDTau}{Sarma et al., 2016}), archiving and deployment of data, code and reports (\emph{e.g.}, this manuscript, \protect\hyperlink{ref-SirQKFIz}{White et al., 2018}), and the interpretation, integration and usage of data and software across different sources (see \protect\hyperlink{ref-1FJhfqfiX}{Pasquier et al., 2017}).
In this context, small modifications to code and data can be frequently committed and automatically tested, as in continuous integration and continuous deployment practices (\protect\hyperlink{ref-1Ep9EJL6y}{Meyer, 2014}).
This allows for early detection and correction of errors, potentially improving confidence in scientific development by minimizing software errors (see \protect\hyperlink{ref-ufw0ZdnI}{Soergel, 2015}).
In addition to increasing scientific rigour and confidence in ecological software (\protect\hyperlink{ref-12103x16N}{Scheller et al., 2010}), automation can help advance more rapidly sharing ecological data and making sure the data are high quality (\protect\hyperlink{ref-rTbinQMj}{Dietze et al., 2018}).
Integrating automation workflows has been highly encouraged in areas of EEB, including predictive ecology (\protect\hyperlink{ref-mmCOSRfr}{McIntire et al., 2022}), long-term ecological studies (\protect\hyperlink{ref-RxK4CmfR}{Ernest et al., 2018}; \protect\hyperlink{ref-1CJo8lo2v}{Yenni et al., 2019}), and management of species at risk information (\protect\hyperlink{ref-kZzfmBNu}{Naujokaitis-Lewis et al., 2022}).

Automation can be integrated into GitHub repositories through the GitHub Actions feature (\protect\hyperlink{ref-NUXbp429}{\emph{Features • GitHub Actions}, n.d.}), or through alternative automation systems (\emph{e.g.}, Circle CI, \protect\hyperlink{ref-T03Api6e}{\emph{Continuous Integration and Delivery}, n.d.}); Travis CI, \emph{Home -- Travis-CI} (\protect\hyperlink{ref-YeFSbfFV}{2022}){]}.
Users can set up workflows associated with their repositories that are triggered by events (\emph{e.g.}, push, pull request or at specified times) for remote servers to perform user-specified steps and actions.
These actions are highly configurable and have numerous applications, such as automatically running analyses and creating figures when data or code are updated, incorporating changes to websites or applications, testing modifications to software (\emph{e.g.}, R or Python libraries).
Action workflows can be found in GitHub's Marketplace (\url{https://github.com/marketplace?type=actions}) or, alternatively, in open user repositories.

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.0000}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Ten tips for getting started in GitHub
\end{minipage} \\
\midrule()
\endhead
1. \textbf{Check for existing solutions to your problem.} The GitHub Help webpage (\url{https://docs.github.com/en}) contains extensive and detailed documents with helpful screenshots. It is a good starting point for handling an issue, and has troubleshooting tips for specific problems. Alternatively, consider Tweeting your issue. There is a large community of GitHub users around the world who have likely faced analogous problems and may be able to provide quick solutions. Third, try to follow blogs (\emph{e.g.}, \url{https://github.blog}), Twitter accounts or YouTube channels that regularly post practical solutions about the most widely-used web platform for common GitHub issues. \\
2. \textbf{Consider taking free courses}, such as those from Software Carpentry (\protect\hyperlink{ref-pjy75gHr}{Madicken Munk et al., 2019}), and sharing them with your lab members or colleagues. \\
3. \textbf{Take advantage of GitHub as an asynchronous working tool for team-based projects.} See the repository for this paper (\url{https://github.com/SORTEE-Github-Hackathon/manuscript}) as an example of a collaboratively authored manuscript that used the GitHub Discussions, Issues, Pages, and Actions features. \\
4. \textbf{Use the interactive courses from the GitHub Skills page (\url{https://skills.github.com/})}, which allow you to learn GitHub basics through short projects and tasks with step-by-step guides. \\
5. \textbf{Learn markdown and use cheatsheets (\emph{e.g.}, \url{http://markdownguide.org/basic-syntax})} so you can write clear metadata README files for your repositories. \\
6. \textbf{Consult online resources.} The Jenny Bryan Universe of GitHub material, for example, provides a thorough and accessible introduction for a multitude of research-related uses for GitHub, and includes a book (\protect\hyperlink{ref-ZvrOcg9w}{Hester, n.d.}), statistics course (\protect\hyperlink{ref-6CMMeSeD}{Bryan \& TAs, n.d.}) and academic article (\protect\hyperlink{ref-RVetqmsg}{Bryan, 2018}). \\
7. \textbf{Do not be afraid of trial-and-error.} One of the best ways to learn GitHub is the ``trial-and-error'' method. Learning from your own mistakes can be a valuable way to master your GitHub abilities. In any case, if you make mistakes, GitHub allows you to revert any steps that you desire via version controlling. \\
8. \textbf{If you are an educator, include lectures on reproducibility and tools for creating reproducible workflows in the curricula.} Some graduate programs include coursework on course R Markdown and GitHub. Getting students started with these tools earlier will prevent the resistance that comes from working with a less reproducible workflow for a longer period of time (see example \url{https://github.com/rmcelreath/stat_rethinking_2022}). \\
9. \textbf{Try to begin committing with graphical user interfaces (GUI) instead of command line interfaces (CLI).} Examples of GUI are the GitHub Desktop (\url{https://desktop.github.com}), git-gui (\url{https://git-scm.com/docs/git-gui}), RStudio (\url{https://www.rstudio.com}), Visual Studio Code (\url{https://code.visualstudio.com}), Atom (\url{https://atom.io}), GitKraken (\url{https://www.gitkraken.com}). \\
10. \textbf{Get help deciphering GitHub Notifications.} Try using tools like Octobox (\url{https://octobox.io}) to disentangle and manage multiple notifications from distinct GitHub projects. \\
\bottomrule()
\end{longtable}

@@

\caption{A comparison of technologies commonly used for collaborating on research in Ecology and Evolutionary Biology. In the first column, we group platforms for collaboration into broad guilds. The second column lists the platform for collaboration. The remaining columns indicate whether the platform for collaboration includes certain features. \label{tbl:compare}}\label{tbl:compare}\tabularnewline
\toprule()

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0493}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1425}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1041}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1562}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1096}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1479}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1370}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1534}}@{}}
\caption{A non-exhaustive collection of ideas for how various GitHub
features could be utilized for a research project. Here we have
categorized contributors/collaborators into five roles. A Project
Manager owns the GitHub repository for a project, and leads the academic
project (e.g., lead author of a manuscript). A co-author contributes to
writing and other aspects of research, but may have limited or no
experience with programming, git, and/or GitHub. A code contributor
writes or edits analysis code for the project. A code reviewer could be
a project collaborator or a peer reviewer who reviews project code. They
are familiar with coding, but not necessarily with git or GitHub (but
they are willing to learn). Finally, community members could be other
researchers or non-researchers interested in reproducing results,
re-using code or data, or communicating with researchers involved in the
project. These roles are not mutually exclusive---a co-author could also
be a code contributor and code reviewer, for example. For definitions of
the GitHub features, see Box 1. \label{tbl:roles}}\label{tbl:roles}\tabularnewline
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Role
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
GitHub repository
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
README
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Issue
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Discussion
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Pull Request
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Fork
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
GitHub Pages
\end{minipage} \\
\midrule()
\endfirsthead
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Role
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
GitHub repository
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
README
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Issue
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Discussion
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Pull Request
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Fork
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
GitHub Pages
\end{minipage} \\
\midrule()
\endhead
Project manager & Set contributor permissions, share code of conduct & Project description, citation, DOIs & Assign tasks to collaborators & Discuss project directions and goals & Approve and incorporate edits to code and/or writing & & Share up-to-date reports, figures, or draft manuscript \\
Co-author & Edit Markdown text or add files & & Propose changes involving code (e.g.~analyses, figures) & Discuss proposed changes to manuscript & & & \\
Code contributor & & & Suggest code changes & & Contribute changes to code, initiate code review & & Contribute to project website \\
Code reviewer & Find all code related to a project & & Highlight specific lines of code and make suggestions & & Review or recommended changes in code & & \\
Community & & & Suggest additional features and report bugs & Ask questions about data and code & & Create a linked, editable copy of the repository & View project website \\
\bottomrule()
\end{longtable}

@@

\leavevmode\vadjust pre{\hypertarget{ref-TOsASkn5}{}}%
\emph{Adding a license to a repository}. (n.d.). GitHub Docs. Retrieved March 4, 2023, from \url{https://ghdocs-prod.azurewebsites.net/en/communities/setting-up-your-project-for-healthy-contributions/adding-a-license-to-a-repository}

\leavevmode\vadjust pre{\hypertarget{ref-13QX8XU3J}{}}%
Alston, J. M., \& Rick, J. A. (2021). A Beginner\textquotesingle s Guide to Conducting Reproducible Research. \emph{The Bulletin of the Ecological Society of America}, \emph{102}(2). \url{https://doi.org/10.1002/bes2.1801}

@@

\leavevmode\vadjust pre{\hypertarget{ref-1HZdsK5Kn}{}}%
Baker, M. (2016). 1,500 scientists lift the lid on reproducibility. \emph{Nature}, \emph{533}(7604), 452--454. \url{https://doi.org/10.1038/533452a}

\leavevmode\vadjust pre{\hypertarget{ref-Qh7xTLwz}{}}%
Beaulieu-Jones, B. K., \& Greene, C. S. (2017). Reproducibility of computational workflows is automated using continuous analysis. \emph{Nature Biotechnology}, \emph{35}(4), 342--346. \url{https://doi.org/10.1038/nbt.3780}

@@

\leavevmode\vadjust pre{\hypertarget{ref-T03Api6e}{}}%
\emph{Continuous Integration and Delivery}. (n.d.). CircleCI. Retrieved March 4, 2023, from \url{https://circleci.com/}

@@

\leavevmode\vadjust pre{\hypertarget{ref-NOgBWVAr}{}}%
Culina, A., van den Berg, I., Evans, S., \& Sánchez-Tójar, A. (2020). Low availability of code in ecology: A~call for urgent action. \emph{PLOS Biology}, \emph{18}(7), e3000763. \url{https://doi.org/10.1371/journal.pbio.3000763}
